---
title: "Movies analysis project"
author: "M-husnain"
date: "18 November 2018"
output: html_document
---

## Setup

### Load packages
```{r load-packages, message = FALSE}
library(ggplot2)
library(dplyr)
library(statsr)
library(oilabs)
```

```{r load-data}
load("movies.R")
summary(movies)
```
## Part 1: Data

To be able to describe how the observations in the data are collected, whether they were random or not,
we have to perform the Residual Plot test. We plot the Residuals and we check if there is a time series
or any kind of patterns associated with it. Because the independent residuals implies an independent 
observations. We can also check the following to check the generalizibility of the model inference
1.Linear Relation between 'X' and 'Y' 
2.Nearly Normal Residuals
3.Constant Variability of Residuals
Since the data was Randomly Sampled, it would be a great fit for a generalized model...

In the absence of a time series pattern, we know that the data comes from Random Sampling and  this Random Sampling eliminates the possibility of a Causal Relationship between Explanatory Variables.

## Part 2: Research Question

#Question: To Predict the Audience score of a movie based on the 
#1.Movie Genre
#2. The production company
#3. The critics score
#4.whether or not one of the main actors in the movie ever won an Oscar
#5.Whether or not one of the main actress in the movie ever won an Oscar
#6.Whether or not the director of the movie ever won an Oscar
#7.  Whether or not the movie is in the Top 200 Box Office list on BoxOfficeMojo
#8. The Mpaa rating of the Movie
#9. The imdb score


# Question no. 3 EDA 

# First of all, I will show the dependence of the score prediction on each of the outlined Feature is a significant predictor of the response variable, that is if it's p-value is significant predictor of the response variable.


``` {r genre}

Genre<-lm(movies$audience_score ~ movies$genre)
summary(Genre)

qqnorm(Genre$residuals)
qqline(Genre$residuals)  
plot(Genre$residuals ~ Genre$fitted)


```

``` {r studio }

Production_studio<-lm(movies$audience_score ~ movies$studio)
summary(Production_studio)

qqnorm(Production_studio$residuals)
qqline(Production_studio$residuals)  
plot(Production_studio$residuals ~ Production_studio$fitted)



```


``` {r Actor_wins_oscar }

Actor_wins_oscar<-lm(movies$audience_score ~ movies$best_actor_win)
summary(Actor_wins_oscar)

qqnorm(Actor_wins_oscar$residuals)
qqline(Actor_wins_oscar$residuals)  
plot(Actor_wins_oscar$residuals ~ Actor_wins_oscar$fitted)





```



``` {r Actress_win_oscar }

Actoress_wins_oscar<-lm(movies$audience_score ~ movies$best_actress_win)
summary(Actoress_wins_oscar)

qqnorm(Actoress_wins_oscar$residuals)
qqline(Actoress_wins_oscar$residuals)  
plot(Actoress_wins_oscar$residuals ~ Actoress_wins_oscar$fitted)





```



``` {r mpaa_rating }

Mpaa_catagory<-lm(movies$audience_score ~ movies$mpaa_rating)
summary(Mpaa_catagory)

qqnorm(Mpaa_catagory$residuals)
qqline(Mpaa_catagory$residuals)  
plot(Mpaa_catagory$residuals ~ Mpaa_catagory$fitted)


```



``` {r top200 }

movie_in_top_200<-lm(movies$audience_score ~ movies$top200_box)
summary(movie_in_top_200)

qqnorm(movie_in_top_200$residuals)
qqline(movie_in_top_200$residuals)  
plot(movie_in_top_200$residuals ~ movie_in_top_200$fitted)




```


``` {r imdb_rating }

Rated_by_imdb<-lm(movies$audience_score ~ movies$imdb_rating)
summary(Rated_by_imdb)

qqnorm(Rated_by_imdb$residuals)
qqline(Rated_by_imdb$residuals)  
plot(Rated_by_imdb$residuals ~ Rated_by_imdb$fitted)




```

``` {r Director_wins_oscar }

Director_wins_oscar<-lm(movies$audience_score ~ movies$best_dir_win)
summary(Director_wins_oscar)

qqnorm(Director_wins_oscar$residuals)
qqline(Director_wins_oscar$residuals)  
plot(Director_wins_oscar$residuals ~ Director_wins_oscar$fitted)




```




``` {r Score_critics }

Critics_score<-lm(movies$audience_score ~ movies$critics_score)
summary(Critics_score)

qqnorm(Critics_score$residuals)
qqline(Critics_score$residuals)  
plot(Critics_score$residuals ~ Critics_score$fitted)



```


# Question no.4 
# Modeling
# For this purpose, we choose a Backward Elimination Approach... We start by a model which has all the Explanatory variables and then reduce one explanatory variable at each step...
# We shall select only that model which  shows the highest increase in the adjusted R-Squared value ...


``` {r  multiple_regression_model}



ml_model <- lm(movies$audience_score~movies$genre+movies$studio+movies$best_actress_win+movies$imdb_rating+movies$best_dir_win+movies$critics_score)
summary(ml_model)

 Steps explained in the backward elimination Mechanism
  
Step 1 : When we include all the selected variables, we get an adjusted R-squared value of 0.7665 #while the Multiple R-squared value is  0.8502.

 Step 2 : When we remove the variable genre, that is, if the genre of the movie, the Adjusted R-Squared value decreases to 0.7571 so we maintain this variable.



 Step 3 : When we remove the variable studio, that is, the production studio that created the movie, the Adjusted R-Squared value decreases to 0.7635, so we maintain this variable.

  Step 4 : When we remove the variable best_actor_win, that is, if the first lead actor ever won an oscar, the Adjusted R-Squared value increases to 0.7669.


 Step 5 : When we remove the variable best_actress_win, that is, if the first lead actress ever won an oscar, the Adjusted R-Squared value decreases  to 0.7657 . so we maintain this variable in our model


 Step 6 : When we remove the variable mpaa_rating, that is, the rating by the Mpaa Authority, the Adjusted R-Squared value increases  to 0.7683 . so we remove this variable in our model

 Step 7 : When we remove the variable top_200box, that is, Whether or not the movie is in the Top 200 Box Office list on BoxOfficeMojo (no, yes), the Adjusted R-Squared value increases  to 0.7688 . so we remove this variable in our model


 Step 8 : When we remove the variable imdb_rating ,that is the  Rating on IMDB
 the Adjusted R-Squared value decreases  to 0.5255 . so we maintain this variable in our model
 This sharp decrease indicates that this is a very important variable in our model


 Step 9 : When we remove the variable best_dir_win ,that is ,if the movie director ever won an oscar,
 the Adjusted R-Squared value decreases  to 0.7683 . so we maintain this variable in our model


 Step 10 : When we remove the variable critics_score,that is ,Critics score on Rotten Tomatoes,
 the Adjusted R-Squared value decreases  to 0.767 . so we maintain this variable in our model


So our final model contains the following variables
1. Genre
2. studio
3. Best Actress win
4. IMdb rating
5. Critics score
6. Best Director win





Question no. 5
Prediction


We will Pick a movie from 2016 (a new movie that is not in the sample) and do a prediction for this #movie using your the model that I developed .
I will also quantify the uncertainty around this prediction using an appropriate interval.

```{r predict}

film <- data.frame(title ="The Pursuit of Happyness", genre="Drama",best_dir_win="no", studio="Overbrook Entertainment",best_actress_win="no", imdb_rating=8,mpaa_rating="PG-13", critics_score =  6.4)
predict(ml_model, film, interval = "prediction", level = 0.95)
```


```{r question-6}
Question no. 6
Key Findings
1. The imdb rating is the most significant predictor of the audience score because removing it from our model causes the R-squared value to decrease sharply from 0.78 to 0.5
2. Sometimes, the assumptions we make is this model might not prove to be significant and may depend on the viewer's behavior.
3. The Sampling of the data should be independent and if it's not, the model will give us biased results which can greatly affect our predictions.
4. One variable which was not included in our data set is the behavior of the audience of a certain area or locality. It is observed that the audience in a certain locality might be attracted to like only a certain genre's or there choices are according to their local Super stars... So this factor should be considered to predict the user's ratings.


```